Implementation of an Open-Source modular mangetic field camera for usage in Low-Field MRI Systems\\

### 2023-10-09 documentation/paper/main.tex
.

\subsection{Communication Bus}
% possible bus systems

@@

%-----------------------------------------------------------------------------------------------------------------------------------------------
% Embedded System Software
\section{Embedded System Software}

\subsection{Automatic Sensor Numbering}

>>>>

\subsection{Communication Bus}
To ensure modularity and easy expandability of the sensor system, it is necessary to be able to integrate several sensors into the system.
On the electrical level, a CAN bus was implemented to connect the individual microprocessors to which up to 16 magnetic field sensors can be digitally connected to an overall system.

In addition to the bus system, the supply voltage and a separate synchronisation signal are necessary to enable automatic recognition of connected sensors. This is connected in a daisy chain between the modules.

@@

\subsection{Powermanagement}
sensor on off

\subsection{}
%-----------------------------------------------------------------------------------------------------------------------------------------------
% Embedded System Software
\section{Embedded System Software}

\subsection{Automatic Sub-Sensor Detection}
